### 2023-02-11 main/frontmatter.tex
abstract tweaks

\begin{abstract}
Searching for new phenomena is an essential endeavour of experimental physics,
and is helped by guidance from plausible theoretical predictions.
This thesis presents such a search for signals of high-energy protons
scattering to massive resonances with dramatic decays, which are predicted by
supersymmetric models~\cite{atlas2022searches}.

No new phenomena appear in the results, so they support the Standard Model in
its continuing successful extrapolation to describe the most extreme behaviours
of proton collisions.
Supersymmetry as a concept as not falsified by this lack of new phenomena,
nor by the many similar observations.
But it is also not confirmed.

@@

\begin{acknowledgements}
Warning: many thank-yous incoming.
Friends and family made these years worthwhile:
mu deepest love and thanks to all of you who have come and gone.

>>>>

\begin{abstract}
Searching for new phenomena is an essential endeavour of experimental physics,
and is helped by guidance from plausible theoretical predictions.
This thesis presents such a search for signals of high-energy protons
scattering to massive resonances with dramatic decays, which are predicted by
supersymmetric models.%
% hack: hidden reference to constrain the reference numbering
\sbox0{\cite{atlas2022searches}}

No new phenomena appear in the results, so they support the Standard Model in
its continuing successful extrapolation to describe the most extreme behaviours
of proton collisions.
Supersymmetry as a concept is not falsified by this lack of new phenomena,
nor by the many similar observations.
But it is also not confirmed.

@@

\begin{acknowledgements}
Warning: many thank-yous incoming.
Friends and family made these years worthwhile:
my deepest love and thanks to all of you who have come and gone.
